---
title: "Solving the canonical New-Keynesian model with lrem"
author: "Akira Matsui"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The following three equation models called the canonical New-Keynesian(NK) model:

**Phillips curve (AS curve)**

$$\pi_{t}	=\beta\mathbb{E}_{t}\pi_{t+1}+\kappa x_{t}+u_{t}^{S}$$

**IS curve**
$$x_{t}=\mathbb{E}_{t}x_{t+1}-\frac{1}{\sigma}\left(i_{t}-\mathbb{E}_{t}\pi_{t+1}\right)+u_{t}^{D}$$

**Monetary policy(MP) rule**
$$
i_{t}=\alpha\pi_{t}+\iota x_{t}
$$


Assume AR shocks with $|\rho_{S}|$, $|\rho_{D}|<1$, $\mathbb{E}_{t}\epsilon_{t+1}^{S}=0$, and $\mathbb{E}_{t}\epsilon_{t+1}^{D}=0$: 

$$
\begin{aligned}
  u_{t+1}^{S}	&=\rho_{S}u_{t}^{S}+\epsilon_{t+1}^{S}\\
  u_{t+1}^{D}	&=\rho_{D}u_{t}^{D}+\epsilon_{t+1}^{D}
\end{aligned}
$$

* $\pi_{t}$: log inflation rate
* $x_{t}$: output gap
* $i_{t}$: log gross nominal interest rate
* $\sigma$: intertemporal elasticity of substitution
* $\beta$: discount rate
* $\kappa$: slope of the Phillips curve
* $\alpha$ and $\iota$: monetary policy parameters



All three endogenous variables, $\pi$, $x$ and $i$, are non-predetermined.

## Matrix


By sumarizing three equations(AS curb, IS curb and MP rule) and two AR shocks, we we obtain the following linear system.

$$  
  \begin{aligned}
    \pi_{t}	&=\beta\mathbb{E}_{t}\pi_{t+1}+\kappa x_{t}+u_{t}^{S}\\
    x_{t} &= \mathbb{E}_{t}x_{t+1}-\frac{1}{\sigma}\left(i_{t}-\mathbb{E}_{t}\pi_{t+1}\right)
    +u_{t}^{D}\\
    i_{t} &=\alpha\pi_{t}+\iota x_{t}\\
    u_{t+1}^{S}	&=\rho_{S}u_{t}^{S}+\epsilon_{t+1}^{S}\\
    u_{t+1}^{D}	&=\rho_{D}u_{t}^{D}+\epsilon_{t+1}^{D}
  \end{aligned}
$$

By using the matrix definition of `lrem` package, the above five equation can be re-written as follow.

\[
\tilde{E}X_{t+1}=\tilde{A}X_{t}+\epsilon_{t+1}
\]

Where, 

\[
\phi\equiv\left[\begin{array}{cc}
\rho_{d} & 0\\
0 & \rho_{s}
\end{array}\right],\ B\equiv\left[\begin{array}{cc}
-1 & 0\\
0 & -1\\
0 & 0
\end{array}\right],\ A\equiv\left[\begin{array}{ccc}
1 & 0 & \frac{1}{\sigma}\\
\kappa & -1 & 0\\
\iota & \alpha & -1
\end{array}\right],\ E=\left[\begin{array}{ccc}
1 & \frac{1}{\sigma} & 0\\
0 & \beta & 0\\
0 & 0 & 0
\end{array}\right]
\]


\[
\tilde{A}\equiv\left[\begin{array}{cc}
\phi\\
B & A
\end{array}\right]=\left[\begin{array}{ccccc}
\rho_{d}\\
 & \rho_{s}\\
-1 &  & 1 &  & \frac{1}{\sigma}\\
 & -1 & \kappa & -1\\
 &  & \iota & \alpha & -1
\end{array}\right],\ \tilde{E}\equiv\left[\begin{array}{cc}
I\\
 & E
\end{array}\right]=\left[\begin{array}{ccccc}
1\\
 & 1\\
 &  & 1 & \frac{1}{\sigma}\\
 &  &  & \beta\\
\\
\end{array}\right]
\]


\[
X_{t}=\left[\begin{array}{c}
u_{t}^{d}\\
u_{t}^{s}\\
x_{t}\\
\pi_{t}\\
i_{t}
\end{array}\right],\ \epsilon_{t}=\left[\begin{array}{c}
\varepsilon_{t}^{d}\\
\varepsilon_{t}^{s}\\
0\\
0\\
0
\end{array}\right].
\]



## Parameters and coefficient matrices

We will use the following parameter values.


```{r}
alpha <- 2
iota <- 0
beta <- 0.99
sigma <- 1
kappa <- 0.132
rhoS <- 0.9
rhoD <- 0.9
```

The matrices $\tilde{E}$, $\tilde{A}$, $B$, $\phi$ are given by

```{r}
E = matrix(0, 3, 3)
A = matrix(0, 3, 3)
B = matrix(0, 3, 2)
Phi = matrix(0, 2, 2)

E[1, 1] = 1
E[1, 2] = 1/sigma
E[2, 2] = beta 

A[1, 1] = 1
A[1, 3] = 1/sigma
A[2, 1] = kappa
A[2, 2] = - 1
A[3, 1] = iota
A[3, 2] = alpha
A[3, 3] = -1

B[1, 1] = 1
B[2, 2] = 1

Phi[1, 1] = rhoD
Phi[2, 2] = rhoS

```

```{r}
E
A
B
Phi
```

```{r}
library("lrem")
library("ggplot2")
```

```{r}
#caluculte policy functions and impulus response
policy <- lre_ar(A, E, B, Phi, nx = 0)

steps <- 100
out <- impulse(policy$g, policy$h, x0 = c(0,0), steps, e1 = c(-1,0))
```

```{r}
#plotting result
result <- data.frame(out)
names(result) <- c("dmand.shock", "supply.shock", "outcome.gap", "inflation", "nominal.interest")
result["t"] <- 0:(steps - 1)
```

```{r}
ggplot(result) + geom_line(aes(x = t, y = dmand.shock)) +  ylab("Demand Shock")
```

```{r}
ggplot(result) + geom_line(aes(x = t, y = supply.shock)) + ylab("Supply Shock")
```

```{r}
ggplot(result) + geom_line(aes(x = t, y = outcome.gap))  + ylab("Output Gap")
```

```{r}
ggplot(result) + geom_line(aes(x = t, y = inflation))  + ylab("Nominal Interest Rate")
```

```{r}
ggplot(result) + geom_line(aes(x = t, y = nominal.interest)) + ylab("Inflation")
```
